---
title: "Exercise 23"
author: "Marc Dotson"
format: docx
---

1. Run a topic model with three topics in `roomba_reviews`.
2. Visualize the topics and name them. Justify your names.
3. Render the Quarto document into Word and upload to Canvas.

**Five points total, one point each for:**

- **Tokenizing Review into words.**
- **Using cast_dtm() to create a DTM.**
- **Running LDA with k = 3.**
- **Visualizing and naming the topics, with justification for each name.**
- **Submitting a rendered Word document.**

## Run a Topic Model

```{r}
# Load packages.
library(tidyverse)
library(tidytext)
library(topicmodels)

# Import data, tokenize, remove stop words, cast a DTM, run a topic model.
set.seed(42)
fit_lda3 <- read_csv(here::here("Data", "roomba_reviews.csv")) |>
  mutate(review_id = row_number()) |> 
  unnest_tokens(word, Review) |> 
  anti_join(stop_words, join_by(word)) |> 
  count(word, review_id) |>
  cast_dtm(review_id, word, n) |> 
  LDA(k = 3, method = "Gibbs")
```

## Name the Topics

```{r}
# Visualize the topics.
fit_lda3 |> 
  tidy(matrix = "beta") |> 
  group_by(topic) |> 
  top_n(10, beta) |>
  ungroup() |>
  mutate(term = reorder_within(term, beta, topic)) |>
  ggplot(aes(x = beta, y = term, fill = as.factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```

Let's name the topics.

- **Features**: This topic is highest on `roomba` and `880` and the features associated with the features of a robotic vacuum: `cleaning`, `clean`, `vacuum`, `battery`. This seems positive overall.
- **Flaws**: This topic is highest overall on the `time`, `floor`, `house`, `clean`, and `stuck` -- all possible flaws or pain points with robotic vacuums.
- **Functions**: This topic is highest overall on `hair`, `floors`, `love`, `dog`, and `dirt` all part of the function of robotic vacuums and likely positive overall.

